Multi-level modelling with Openflexo/\FML - A contribution to the \mpc

### 2021-05-28 8-Discussion.tex
few todos (assessment part)

  The Openflexo approach is level-agnostic: ``levels'' have no specific
  nature and there are no numbered levels.

\todo[inline]{mais on peut dire que les niveaux sont empaquetés dans des virtual models ; pour passer d'un niveau à l'autre, on a des relations : héritage et instantiation}

@@

  \subsection{Cross-level relashionships}

@@

  Thanks to the level-agnosticity nature of the Openflexo approach, cross-level
  relashionships are not an issue. Model elements of different levels can be
  linked each other in a transparent way. %If the user has defined
  %well-formedness constraints, then they are

@@

  Behaviors are continuously checked, ensuring the integrity of the models when changes occur. 
  However, most of those behaviors have to be written by the users. 
  Thus, the integrity of the contents relies on the users when they build the metamodels and the models.
  Note that in our approach, the metamodels are built in a ad hoc way together with the models
  (co-construction), therefore the user also validates on a ad hoc basis.

@@

  Due to the level-agnostic aspect of our approach, we could insert a new level,
  for example. It would consist in creating new concepts we would link to
  other ones. Then, we would add any necessary constraints on those concepts
  and on the relashiontips linking them to the other existing concepts.

>>>>

  The Openflexo approach is level-agnostic: ``levels'' have no specific nature
  and there are no numbered levels. In our solution, concepts of a given level
  are grouped into a virtual model. Inheritance and instantiation allow the
  establishment of relationships between concepts from different levels.

%\todo[inline]{mais on peut dire que les niveaux sont empaquetés dans des virtual models ; pour passer d'un niveau à l'autre, on a des relations : héritage et instantiation}

@@

  \subsection{Cross-level relationships}

@@

  Thanks to the level-agnosticity nature of the Openflexo approach, cross-level
  relationships are not an issue. Model elements of different levels can be
  linked each other in a transparent way, using inheritance or instantiation.

@@

  Behaviors are continuously checked, ensuring the integrity of the models when
  changes occur. However, most of these behaviors have to be written by the
  users. Thus, the integrity of the contents relies on the users when they
  build the metamodels and the models.  Note that in our approach, the
  metamodels are built in a ad hoc way together with the models
  (co-construction), therefore the user also validates on a ad hoc basis.

@@

  Due to the level-agnostic aspect of our approach, we could insert a new
  level, for example. It would consist in creating new concepts we would link
  to other ones. Then, we would add any necessary constraints on those concepts
  and on the relationships linking them to the other existing concepts.
